\documentclass[10pt,courier]{navymemo}

\author{Dennis Evangelista}
\title{Letter of recommendation ICO MIDN 2/C C Stites}
\navysubj{Letter of recommendation ICO MIDN 2/C C Stites}
%\navyfiling{5200.1}
%\navyserial{16-0001}
\date{\today}
%\navymarking{UNCLASSIFIED}

\usepackage{designature}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{Asst Prof Evangelista}
\navyto{Bowman Scholarship Selection Committee}
\navyskip{}%
\navysubjline{}%
\end{navyletterheader}

%Involved in activities outside the classroom.
%You think I would be a good candidate to effectively use the opportunity of being a Bowman Scholar.

\section{} 
I am happy to recommend MIDN 2/C Corwin Stites for a Bowman Scholarship.  I was one of Stites' instructors and was previously a Naval Reactors engineer in 08E, where I worked on advanced submarine systems and deep submergence. Stites is an outstanding midshipman who embodies academic excellence, evidenced by his 4.0 QPR. Stites has great potential for graduate study at NPS, and is motivated to serve in submarines.  

\section{}
I was Mr.~Stite's instructor in EW202 (Principles of Mechatronics).  All of our Robotics and Controls Engineering majors take classes in computer science, electrical engineering, mechanical engineering, and controls with a heavy emphasis on skills needed to enable future autonomous naval systems. In EW202, Stites stood above all others with a 100\% on the final exam and an A overall in the class. He also successfully developed autonomous behaviors for a rover navigating a channel while avoiding magnets embedded beneath within it, using a suite of color, ultrasonic range, and Hall-effect sensors and a small ARM-based microcontroller. 

\section{}
Mr.~Stites wishes to study Electrical/Electronic System Engineering at NPS. I believe he will be very succesful in this field. Stites is passionate about engineering and an eager participant in class. The research proposal he has been developing has great potential for future undersea autonomous warfare; a future where manned submarines will be teamed with unmanned assets, and we as well as our opponents may have to operate (underwater; surface; and aerial) swarms in tight areas where connectivity, bandwidth, and logistics are concerns. The passion Stites has shown in learning about the background and setting up his research questions bodes well for his aptitude to contribute something exciting and relevant. 

\section{}
Mr.~Stites' planned project makes good use of modeling and simulation and the unique features Hopper Hall will have regarding hardware UUV studies. It also connects with summer work done at internships, fits with topics he would study at NPS, and is of interest and timely relevance to the nuclear Navy. 

%\respectfully{}
\noclosing{}
\signature{\includesignature}
\signature{D EVANGELISTA}

\end{document}